---
title: "Biker_project"
author: "derek"
date: '2022-06-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This document will receive the sql export as an input and draw some graphs that could lead to insights of the current situations and markets or the biking company


## Importing the data and activating library

You can activate libraries after installing packages, for example:

```{r library, eval=FALSE}
library(tidyverse)
library(ggplot2)
```

Then we import the data and specify the column names
```{r import}
library(tidyverse)
test1 <-read_csv("test2.csv", col_names = c("rideid", "ridetype", "membership","time","dayofweek"))
```

Check the structure of the data frame

```{r head1}
head(test1)
colnames(test1)
```


## Plotting some graphs
See the relationship between ride type and membership
```{r head}
ggplot(data = test1) +
  geom_bar(mapping= aes(x = membership,fill = ridetype))
```

See the average time of each membership
Average ride time of casual members is twice of formal members


```{r average time}
ggplot(test1, aes(x = factor(membership), y = time)) + 
  geom_bar(stat = "summary", fun = "mean") +
   scale_y_continuous("time in minutes")
```

Let's see the average time of ride by different days of the week and membership type

```{r group}
newtest <-test1 %>% group_by(membership,dayofweek) %>% drop_na() %>% 
  summarize(mean1 =mean(time))
ggplot(data = newtest) +
  geom_smooth(mapping = aes(x = dayofweek,
                           y = mean1,linetype = membership))
```

As we can see, monday and Sunday for both members and non-members are the days with the longest ride time.



Finally, let's investigate the relationship between riding habits on different days by membership


```{r group1}
ggplot(data = test1) +
  geom_bar(mapping= aes(x = dayofweek,fill  = membership)) + facet_wrap(~membership)

```

As we can see from the graph as well as the sql query, casual members outweigh formal members in Monday and Sunday.
Possible promotion can apply to these days to turn casual into members